Quantifying the Impact \\ of Performance Improvements and Cost Reductions \\ from 20 years of Light-Emitting Diode Manufacturing

### 2021-02-05 SPIE/article/main.tex
finished equations on dis-aggregation

Also to diagreggate contribution of single changes
To dis-aggregate the contribution of changes in manufacturing process steps to total manufacturing cost, we used an approach introduced by Kavlak et al. in a cost model with similar process step resolution for solar photovoltaics. It is based on the logarithmic derivative of the total differential of the cost function.

The following discussion follows an approach developed by Kavlak et al. \cite{kavlak2018evaluating}. For the detailed derivation, we refer to this publication.

    \begin{align}
        C_i(\vec{r}) &= C_i^0 \prod_w g_{iw}(r_w) \\
        \Delta C_x &= \int_{t=t_0}^{t_1} C(t) \frac{ \partial \ln C }{ \partial x } \frac{ \text{d} x }{ \text{d} t} \text{d} t \\
        \Delta C_z (t_1,t_2) &\approx \sum_i \tilde{C_i} \ln \frac{g_{iz}(t_2)}{g_{iz}(t_1)}
    \end{align}

    where

>>>>

    To dis-aggregate the contribution of changes in single variables on total performance in both the device sub-efficiencies and the manufacturing cost, we used an approach introduced by Kavlak et al. \cite{kavlak2018evaluating}. It is based on the logarithmic derivative of the total differential of the cost function. We can write the cost function $C$ of the manufacturing process as a function of a vector of cost model variables $\vec{r}=(r_1,r_2,\dots)$, where $g_{iw}(r_w)$ gives the dependence of $i$th cost component on the $w$th variable. The contribution of changes in the cost model $\Delta C_z$ to total manufacturing cost $C$ can now be approximated. For the detailed derivation, we refer to the supplementary material of the original publication.

	\begin{align}
        C(\vec{r}) &= C(r_1,r_2, \dots) = \sum_i C_i = \sum_i C_i^0 \prod_w g_{iw}(r_w) \\
        \Delta C_x &= \int_{t=t_0}^{t_1} C(t) \frac{ \partial \ln C }{ \partial x } \frac{ \text{d} x }{ \text{d} t} \text{d} t \\
        \Delta C_z (t_1,t_2) &\approx \sum_i \tilde{C_i} \ln \frac{g_{iz}(t_2)}{g_{iz}(t_1)}
    \end{align}
